Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-09-02 final.tex
up

In 2021, \"Ozkan and Würdemann  \cite{DBLP:journals/corr/abs-2108-00889} and \"Ozkan \cite{DBLP:conf/gg/Ozkan22}, in 2022, proved the decidability of the bounded state-resilience problem and the $k$-state-resilience problem for WSTS  with strong compatibility and with the supplementary (strong) hypothesis that there exists an algorithm that computes a finite basis of $\uparrow \post^*(s)$ for all state $s$ (called effective 
$\uparrow$ $\post^*$ basis) and with $\Safe=\uparrow \Safe$ and $\Bad$ downward-closed.

>>>>

In 2021, \"Ozkan and Würdemann  \cite{DBLP:journals/corr/abs-2108-00889} and \"Ozkan \cite{DBLP:conf/gg/Ozkan22}, in 2022, proved the decidability of the bounded state-resilience problem and the $k$-state-resilience problem for WSTS  with strong compatibility and with the supplementary (strong) hypothesis that there exists an algorithm that computes a finite basis of $\uparrow \post^*(s)$ for all state $s$ (called effective 
$\uparrow$ $\post^*$ basis) in the case $\Safe=\uparrow \Safe$ and $\Bad = \downarrow \Bad$.
